### 2016-11-16 paper/modes.tex
Added Fix tag about parallel settings with Maven

\Jbc{I have to understand better how Surefire executes tests. I'm
    afraid it has its own wrapper classes and reuse JUnit core
    functionalities. I'm saying this because JUnit does not offer a
    finer control over thread numbers while this configuration is
possible with Surefire} For example, Figure~\ref{fig:surefire}
illustrates how to configure Maven to execute classes sequentially
(default behavior) and test methods in parallel. Although the setting
are configured on the build file (\eg, \emph{pom.xml} on Maven), these
settings are forwarded to the underlying testing framework (\eg,
JUnit). In case of JUnit,

>>>>

\Jbc{I have to understand better how Surefire executes tests. I'm
afraid it has its own wrapper classes and reuse JUnit core
functionalities. I'm saying this because JUnit does not offer a finer
control over thread numbers while this configuration is possible with
Surefire} For example, Figure~\ref{fig:surefire} illustrates how to
configure Maven to execute classes sequentially (default behavior) and
test methods in parallel. Although this configuration is defined in
the build file (\eg, \emph{pom.xml} on Maven), \Fix{these settings are
forwarded to the underlying testing framework (\eg, JUnit). In case of
JUnit,}
